On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement

### 2023-10-20 manuscript/sections/discussion.tex
manuscript: arXiv version

% On "emissionality" approach
\textbf{Is 24/7~CFE the right strategy? --} Last but not least, it is worth mentioning an ongoing discussion whether 24/7 CFE is the right strategy for companies to reduce their carbon emissions.
Some proponents of alternative strategies contend that 24/7 CFE, or \enquote{temporal matching}, may not represent the most effective approach to emissions reduction. 
This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover own consumption 24/7 with clean electricity is a different strategy to optimising the assets specifically to displace \enquote{as much emissions as possible}.

@@

Another alternative strategy could be that companies do annual matching with \enquote{overprocurement}, i.e., covering own consumption on an annual volumentric basis plus procuring some more clean electricity on top. Such strategy could be implemented at low cost, e.g., with solar PV. 
However, as shown in \cref{subsec:mechanisms}, this strategy would not be as effective in reducing system-level emissions as 24/7 CFE matching, especially in the context of evolving national energy and climate policies.  
Further, such a strategy would not promote innovation and pull forward in time research and investment decisions in advanced energy technologies, such as long-duration energy storage and clean firm generators.

>>>>

% On "emissionality" approach
\textbf{Is 24/7~CFE the right strategy? --} Last but not least, it is worth mentioning an ongoing discussion whether 24/7 CFE is the right strategy for companies to reduce their carbon emissions.
Some proponents of alternative strategies contend that 24/7 CFE, or \enquote{temporal matching}, may not represent the most effective approach to emissions reduction. 
This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover consumption 24/7 with clean electricity is a different strategy to optimising the assets specifically to displace \enquote{as much emissions as possible}.

@@

Another alternative strategy could be that companies do annual matching with \enquote{overprocurement}, i.e., covering their own consumption on an annual volumentric basis plus procuring some more clean electricity on top. Such strategy could be implemented at low cost, e.g., with solar PV. 
However, as shown in \cref{subsec:mechanisms}, this strategy would not be as effective in reducing system-level emissions as 24/7 CFE matching, especially in the context of evolving national energy and climate policies.  
Further, such a strategy would not promote innovation and pull forward in time research and investment decisions in advanced energy technologies, such as long-duration energy storage and clean firm generators.

### 2023-10-20 manuscript/sections/introduction.tex
manuscript: arXiv version

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
The European Union (\gls{eu}) has committed to achieving net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}. 
National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have \co emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.

>>>>

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
The European Union (\gls{eu}) has committed to achieving net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}. 
National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have CO$_2$ emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.
